### 2013-11-08 article2013.Rmd
Regression tables added and pandoc works ok. Booktabs and dcolumn would be nice

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --number-sections -o article2013.pdf")
system("~/.cabal/bin/pandoc -s article2013.md --toc --number-sections -o article2013.html")
system("~/.cabal/bin/pandoc -f markdown -t docx article2013.md -o article2013.docx --standalone --toc --number-sections")
system("~/.cabal/bin/pandoc article2013.md -o article2013.epub --standalone --toc --number-sections")

@@

![Countries used in the analysis](figure/mapplot.pdf)

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),
              type="latex",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top")

@@

```{rrmultilevelMultivarFullOutput, results='asis', eval=TRUE}
load("data/finalModels.RData")

model.names.multi.2 = c("Social blame vs. not",
                      "Individual blame vs. not",
                        "Social blame vs. Individual blame")

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)

@@

<!--

As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.

-->

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --latex-engine=xelatex -o article2013.pdf")

system("~/.cabal/bin/pandoc article2013.md  --number-sections -o article2013.pdf")

system("~/.cabal/bin/pandoc -s article2013.md --toc --number-sections -o article2013.html")
system("~/.cabal/bin/pandoc -f markdown -t docx article2013.md -o article2013.docx --standalone --toc --number-sections")
system("~/.cabal/bin/pandoc article2013.md -o article2013.epub --standalone --toc --number-sections")

@@

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),table.placement="H",
              type="latex",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top",)

@@

*As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.*

```{rarticleModels, results='asis', eval=TRUE}
load("data/finalModels.RData")

model.names.multi.2 = c("SB vs. not",
                      "IB vs. not",
                        "SB vs. IB")

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),float.pos="H",
        use.packages=TRUE,
        #booktabs=TRUE,
        #dcolumn=TRUE,
        #sideways=TRUE, 
        naive = TRUE, 
        caption.above=TRUE,
        doctype=FALSE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation")

@@

### 2013-11-08 finalPlots.Rmd
Regression tables added and pandoc works ok. Booktabs and dcolumn would be nice

# GDP change

@@

t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=gdpchange07.10, 
                        y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5, color="black") +
  geom_text(data=cnames, aes(gdpchange07.10,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
             y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                            y=individualBlame, color=group_general)) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=individualBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for individual blame type of explanation (%)") +
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_gdp.pdf", width=14/2.54, height=10/2.54)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

ppi <- 300
png("figure/scatter_gdp.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=2)
dev.off()
```

@@

# UNU-Wider Gini

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, uw_gini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=uw_gini, y=socialBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=uw_gini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=socialBlame, color=group_general)) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=socialBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, uw_gini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=uw_gini, y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +  
  geom_point(data=t4, aes(x=uw_gini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=individualBlame, color=group_general)) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=individualBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_gini.pdf", width=14/2.54, height=10/2.54)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

ppi <- 300
png("figure/scatter_gini.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=2)
dev.off()
```

@@

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=wbgi_vae, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Voice and Accountability Index 2011", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=socialBlame, color=group_general)) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=socialBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=wbgi_vae, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x ="Voice and Accountability Index 2011", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=individualBlame, color=group_general)) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=individualBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_wbgi.pdf", width=14/2.54, height=10/2.54)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

ppi <- 300
png("figure/scatter_wbgi.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

@@

```{rattribFinalPlotsx, eval=FALSE}

>>>>

# Scatterplots

## GDP change

@@

t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=gdpchange07.10, 
                        y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5, color="black") +
  geom_text(data=cnames, aes(gdpchange07.10,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
             y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=individualBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for individual blame type of explanation (%)") +
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_gdp.pdf", width=14/2.54, height=22/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_gdp.png", width=14/2.54*ppi, height=22/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

## UNU-Wider Gini

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, uw_gini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=uw_gini, y=socialBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=uw_gini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=socialBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, uw_gini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=uw_gini, y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +  
  geom_point(data=t4, aes(x=uw_gini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=individualBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_gini.pdf", width=14/2.54, height=22/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_gini.png", width=14/2.54*ppi, height=22/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

## World Bank - Voice and Accountability

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=wbgi_vae, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Voice and Accountability Index 2011", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=socialBlame,
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=socialBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=wbgi_vae, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x ="Voice and Accountability Index 2011", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=individualBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_wbgi.pdf", width=14/2.54, height=22/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_wbgi.png", width=14/2.54*ppi, height=22/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

@@
